---
title: "One psychometric curve"
output: html_notebook
---
## Standard error

The standard error $se$ of an statistic (a function of the data) $\widehat{\theta}$ is defined as

$$se = \sqrt{V(\widehat{\theta})}$$

The variance could be calculated because $\widehat{\theta}$ is a random variable.

### Standard error for the sample mean if $X$ is distributed normally or $n$ is large (CLM)

 
$$se(\overline{X}_n)=\sqrt{V(\overline{X}_n)} = \frac{\sigma}{\sqrt{n}}$$

### Relation with confidence intervals

A $1 - \alpha$ confidence interval for a parameter $\theta$ is an interval $C_n = (a,b)$ where $a=a(X_1,\dotsc,X_n)$ and $b=b(X_1,\dotsc,X_n)$ are functions of the data such that $P(\theta \in C_n) = 1 - \alpha$.

If $\widehat{\theta_n}$ is distributed $N(\mu, se^2=\sigma^2/n)$ ($\theta$ is normally distributed or CLT) then

$$C_n = (\widehat{\theta_n} - z_{1-\alpha/2} \, se, \widehat{\theta_n} + z_{1-\alpha/2}\, se)$$

if $\alpha = .05$ then 

$$ z_{1-\alpha/2} = 1.96$$
```{r}
qnorm(1 - .025)
```
which gives the famous rule of plus minus two times the standard error. 

If $\sigma^2$ is unknown

then

$$C_n = (\widehat{\theta_n} - t_{1-\alpha/2} \, \widehat{se}, \widehat{\theta_n} + t_{1-\alpha/2}\, \widehat{se})$$

with $\widehat{se}^2=S^2_n / n$

where $S^2_n$ is the sample variance

$$S_n^2=\sum_{i=1}^{n}\frac{(X_i-\overline{X}_n)^2}{n-1}$$


if $\alpha = .05$ and n = 10 then 

$$ t_{1-\alpha/2} = 2.26$$
```{r}
qt(1 - .025, 10 - 1)
```

If n large, we get the same that for known variance
```{r}
qt(1 - .025, 1000 -1)
```

### Nuestro caso

Do we need to use $z$ or $t$. 


```{r message=FALSE}
library(tidyverse)
library(rlang)
library(quickpsy)
library(broom)
library(cowplot)
library(modelfree)
library(psyphy)
library(modelr)

list.files("R", full.names = TRUE) %>% walk(source)
load("logdata/dat_resp.RData")

```

## Select one condition, predict and plot with confidence intervals

Los ci están calculados con z pero no si deben estar calculadoso con t. 
```{r}
dat_resp_one <- dat_resp %>% 
  filter(participant =="01",  platform == "CRT", size == "Small")

prob_one <- calculate_proportions(dat_resp_one, correct, duration) %>% 
  mutate(r = n - k, log10_duration = log10(duration)) %>% 
  ungroup()

model_one <- glm(cbind(k, r) ~ log10_duration, 
             data = prob_one, 
             family = binomial(mafc.probit(2)))

log10_duration_seq_df <- tibble(log10_duration = seq(log10(0.005), 
                                                     log10(.25), 
                                                     length.out = 100))
pre <- augment(model_one, 
               newdata = log10_duration_seq_df,
               type.predict = "response") %>% 
  mutate(fitted_min = .fitted - qnorm(1- .5* .01) * .se.fit, 
         fitted_max = .fitted + qnorm(1- .5* .01)  * .se.fit)

ggplot() +
  geom_ribbon(data = pre, aes(x = log10_duration, ymin = fitted_min, 
                              ymax = fitted_max), fill = "grey") +
  geom_point(data = prob_one, aes(x = log10_duration, y = prob))+
  geom_line(data = pre, aes(x = log10_duration, y = .fitted)) 
```


    
### Obtaining the threshold and ci using quickpsy

```{r message=FALSE}
library(quickpsy)
fit_quick <- quickpsy(prob_one, log10_duration, k, n, guess = .5, B = 300)
fit_quick %>% plot()
```

### Obtaining the the threshold using `glm` 

```{r}
coefi <- model_one %>% tidy() %>% pull(estimate) 

sigma <- 1 / coefi[2]
mu <- -coefi[1] / coefi[2]

coeff <- model_one %>% confint(level = .95)

ci_beta_0 <- coeff[1,]
ci_beta_1 <- coeff[2,]

sigma_min_max <- 1/ ci_beta_1

mu_min_max <- -ci_beta_0 / ci_beta_1

mu_min_max_df <- tibble(xmin = mu_min_max[1], xmax = mu_min_max[2], prob = .75)

ggplot() +
  geom_ribbon(data = pre, aes(x = log10_duration,
                              ymin = fitted_min, ymax = fitted_max),
              fill = "grey") +
  geom_point(data = prob_one, aes(x = log10_duration, y = prob))+
  geom_line(data = pre, aes(x = log10_duration, y = .fitted)) +
  geom_segment(data = tibble(mu, prob = .75), aes(x = mu, xend = mu,
                                                  y = 0, yend = .75, color = "glm")) +
  geom_segment(data = fit_quick$thresholds, aes(x = thre, xend = thre,
                                                  y = 0, yend = .75, color = "quickpsy")) +
  geom_segment(data = mu_min_max_df, aes(x = xmin , xend = xmax, 
                                         y = prob, yend = prob, color = "glm")) +
  geom_segment(data = fit_quick$thresholds, aes(x = threinf , xend = thresup, 
                                                y = prob + .01, yend = prob +.01,
                                                color  = "quickpsy")) 
```

### Significance of the coeficients

```{r}
model_one %>% summary()
```
Or
```{r}
model_one %>% tidy()
```

### Duration does something?

```{r}
model_one %>% anova(test = "Chisq")
```

Yes, adding log10_duration is statistically highly  significant

### Comparing to the null model manually
```{r}
model_one_null <- glm(cbind(k, r) ~ 1, 
             data = prob_one, 
             family = binomial(mafc.probit(2)))

anova(model_one, model_one_null, test = "Chisq")
```

No salen exactamente los mismos numeros pero muy parecidos. 

### DUDA

Por que sale tan diference con anova y summary