---
title: "Two psychometric curves"
output: html_notebook
---

```{r message=FALSE}
library(tidyverse)
library(quickpsy)
library(broom)
library(cowplot)
library(modelfree)
library(psyphy)
library(modelr)

list.files("R", full.names = TRUE) %>% walk(source)
load("logdata/dat_resp.RData")

```

### Select two conditions, predict and plot with confidence intervals
```{r}
dat_resp_two <- dat_resp %>% 
  filter(participant =="04",  platform == "CRT")

prob_two <- calculate_proportions(dat_resp_two, correct, 
                                  duration, size) %>% 
  mutate(r = n - k, log10_duration = log10(duration)) %>% 
  ungroup()

model_two_interaction <- glm(cbind(k, r) ~ size / log10_duration - 1, 
             data = prob_two, 
             family = binomial(mafc.logit(2)))

# Alternatives (Knoblauch) that are the same model:   
# size + size:log10_duration - 1 
# size * log10_duration - log10_duration - 1

log10_duration_seq_size_df <- prob_two %>% distinct(size) %>% 
  crossing(tibble(log10_duration = seq(log10(0.005), 
                                       log10(.25), 
                                       length.out = 100)))

pre_two_interaction <- augment(model_two_interaction, 
               newdata = log10_duration_seq_size_df,
               type.predict = "response") %>% 
  mutate(fitted_min = .fitted - .se.fit, 
         fitted_max = .fitted + .se.fit)

ggplot() +
  geom_point(data = prob_two, 
             aes(x = log10_duration, y = prob, color = size)) +
  geom_line(data = pre_two_interaction, 
            aes(x = log10_duration, y = .fitted, color = size)) 
```

### Doing it for each curve individually
```{r}
model_two_interaction_individually <- prob_two %>% 
  group_by(size) %>% 
  nest() %>% 
  mutate(model = map(data, 
                     ~glm(cbind(k, r) ~ log10_duration, 
                          data = ., 
                          family = binomial(mafc.logit(2)))))
```

We can see that we obtain the same coefficients, with the same standard error, p.values...
```{r}
model_two_interaction %>% tidy()
model_two_interaction_individually$model %>% map(tidy)
```

The sum of the log likelihood, AIC, deviance and df. residual of the separate model corresponds to the all-together model, but not all the glance variables
```{r}
model_two_interaction %>% glance()

model_two_interaction_individually %>% 
  transmute(glance = map(model, glance)) %>% 
  unnest() %>% 
  summarise_all(sum)
```

Augment sale lo mismo para las predicciones y los standard error pero no para todos los valores 
```{r}
model_two_interaction %>% augment() %>% 
  select(-1) %>% #elimino 1a col porque es una matriz y es un rollo  
  arrange(size)

model_two_interaction_individually %>% 
  mutate(augment = map(model, augment), 
         augment = map(augment, select, -1)) %>% 
  select(-data, -model) %>% 
  unnest()
```

### fitting all data with a single psychometric function
```{r}
model_one <- glm(cbind(k, r) ~ log10_duration , 
             data = prob_two, 
             family = binomial(mafc.logit(2)))

log10_duration_seq_df <- tibble(log10_duration = seq(log10(0.005), 
                                       log10(.25), length.out = 100))

pre_one <- augment(model_one, 
               newdata = log10_duration_seq_df,
               type.predict = "response") %>% 
  mutate(fitted_min = .fitted - .se.fit, 
         fitted_max = .fitted + .se.fit)

ggplot() +
  geom_point(data = prob_two, 
             aes(x = log10_duration, y = prob, color = size)) +
  geom_line(data = pre_one, 
            aes(x = log10_duration, y = .fitted))
```

#### Comparing the one psychometric function vs two psychometric functions
```{r}
anova(model_two_interaction, model_one, test = "Chisq")
```
The model with two psychometric functions significantly improves

### Plotting the same slope 

```{r}
model_two_interaction_one_slope <- glm(
  cbind(k, r) ~ size + log10_duration - 1, 
             data = prob_two, 
             family = binomial(mafc.logit(2)))

model_two_interaction_one_slope2 <- glm(
  cbind(k, r) ~ size + log10_duration - 1, 
             data = prob_two, 
             family = binomial(mafc.logit(2)))

pre_two_interaction_one_slope <- augment(
  model_two_interaction_one_slope, 
               newdata = log10_duration_seq_size_df,
               type.predict = "response") %>% 
  mutate(fitted_min = .fitted - .se.fit, 
         fitted_max = .fitted + .se.fit)

pre_two_interaction_one_slope2 <- augment(
  model_two_interaction_one_slope2, 
               newdata = log10_duration_seq_size_df,
               type.predict = "response") %>% 
  mutate(fitted_min = .fitted - .se.fit, 
         fitted_max = .fitted + .se.fit)

ggplot() +
  geom_point(data = prob_two, 
             aes(x = log10_duration, y = prob, color = size)) +
  geom_line(data = pre_two_interaction_one_slope, 
            aes(x = log10_duration, y = .fitted, color = size)) +
    geom_line(data = pre_two_interaction_one_slope2, 
            aes(x = log10_duration, y = .fitted, color = size),
            lty = 2) 
```

Las curvas salen lo mismmo con 

size + lo10_duration - 1 y 
size + lo10_duration 

pero hay cosas que cambian 

#### Comparing same different or same slope para el model con y sin -1
```{r}
anova(model_two_interaction, 
      model_two_interaction_one_slope, test = "Chisq")
anova(model_two_interaction, 
      model_two_interaction_one_slope2, test = "Chisq")
```

El analisis de varianza sale lo mismo 
